Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-08 manuscript/manuscript.Rmd
minor wording updates

A minimum quality standard expected of all scientific manuscripts is that any numerical values can be reproduced if the original analyses are repeated upon the original data [@bollen2015]. This concept is known as *analytic reproducibility* [@lebel2018; or relatedly, *computational reproducibility*[^compRepro], @stodden2018]. When a number cannot be reproduced, this minimally indicates that the process by which it was calculated has not been sufficiently documented. Non-reproducibility may also indicate that an error has occurred, either during the original calculation or subsequent reporting. Either way, there is a breakdown in the integrity of the analysis pipeline that transforms raw data into reported results. As a result, non-reproducibility can create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences. As a result, non-reproducibility can undermine data re-use [@hardwicke2018a], complicate replication attempts [@nuijten2018], and create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences [@lebel2018].

[^compRepro]: Computational reproducibility is often assessed by attempting to re-run original computational code and can therefore fail if original code is unavailable or non-functioning [e.g., @stodden2018]. By contrast, analytic reproducibility is assessed by attempting to repeat the original analysis procedures, which can involve implementing those procedures in new code if necessary [e.g., @hardwicke2018a].

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline typically preclude downstream assessment of analytic reproducibility.

>>>>

A minimum quality standard expected of all scientific manuscripts is that any reported numerical values can be reproduced if the original analyses are repeated upon the original data [@bollen2015]. This concept is known as *analytic reproducibility* [@lebel2018; or relatedly, *computational reproducibility*[^compRepro], @stodden2018]. When a number cannot be reproduced, this minimally indicates that the process by which it was calculated has not been sufficiently documented. Non-reproducibility may also indicate that an error has occurred, either during the original calculation or subsequent reporting. Either way, the integrity of the analysis pipeline that transforms raw data into reported results cannot be guaranteed. As a result, non-reproducibility can create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences. As a result, non-reproducibility can undermine data re-use [@hardwicke2018a], complicate replication attempts [@nuijten2018], and create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences [@lebel2018].

[^compRepro]: Computational reproducibility is often assessed by attempting to re-run original computational code and can therefore fail if original code is unavailable or non-functioning [e.g., @stodden2018; @obels2019]. By contrast, analytic reproducibility is assessed by attempting to repeat the original analysis procedures, which can involve implementing those procedures in new code if necessary [e.g., @hardwicke2018a; @minocher2020].

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline can prevent downstream assessment of analytic reproducibility.
